\documentclass[letterpaper,12pt]{article}

\usepackage[empty]{fullpage}
\usepackage[top=2.5cm, bottom=1.6cm, left=1.9cm, right=1.9cm]{geometry}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{xcolor}
\usepackage{parskip}

\hypersetup{
    colorlinks=true,
    urlcolor=black
}

\definecolor{almost_black}{HTML}{121212}

\setlength{\parindent}{0pt}
\setstretch{1.15}
\setlength{\parskip}{12pt}

\begin{document}
    \color{almost_black}
    
    %--------HEADING--------
    {\fontsize{24pt}{28pt}\selectfont \textbf{Jiayang Dong} \par}
    \vspace{-5.3mm}
    \noindent\rule{\linewidth}{1.5pt}
    \vspace{3mm}
    \href{mailto:dongjiayang123@hotmail.com}{dongjiayang123@hotmail.com} \quad
    672 855 3538

    %--------CONTENT--------
    \vspace{-2.3mm}
    August 12, 2025

    Holman \newline
    1270 Central Parkway West, Suite 600 \newline
    Mississauga, ON

    \textbf{Re: F25 Developer Co-Op 171853B}
    
    Dear Hiring Manager,
     
    I'm a third-year Computer Science student with a passionate interest in software development, and I'm excited to apply for the Developer Co-Op position at Holman. I am drawn to Holman's long-standing commitment to "Driving What's Right" and its role as a global automotive leader, and I am eager to contribute my development skills to your team.
    
    At nwHacks, my team's project Access Buddy won the Potential Community Impact award. I integrated APIs like Vosk, OpenAI, and PyAutoGUI to turn voice commands into web actions, implementing audio input caching and native browser feedback. In CPSC 310, I earned the highest grading category on every project checkpoint with an 86\% final grade, demonstrating my proficiency in TypeScript, React, and full-stack development.
    
    Recently, I’ve been developing a website for Under One Sky, a UBC initiative, using next.js, managing the complete project lifecycle from initial branding and design on Figma to final deployment on Vercel. This experience has taught me that quality web development is an iterative process requiring attention to both technical implementation and user feedback.
    
    My leadership experiences complement my technical skills. As an HR Coordinator with the UBC Science Undergraduate Society, I led the recruitment and training of over 50 volunteers. I also served as an UBC Imagine Day Orientation Leader, helping first-year students feel welcome—both roles sharpened my communication and problem-solving skills.
    
    I am particularly impressed by Holman's focus on evolving its technical standards and its dedication to doing right by its people, customers, and community. I am confident that my skills in modern web technologies, combined with my eagerness to learn, will allow me to contribute effectively. I welcome the opportunity to discuss how my experience aligns with your team's needs. Thank you for considering my application.
    
    Sincerely, \\
    Jiayang Dong 

\end{document}